---
output: 
    github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%",
    eval = TRUE
)
devtools::load_all(".")
```

# dti

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/valid)](https://CRAN.R-project.org/package=valid)
<!-- badges: end -->

## Installation

You can install the development version of from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("rappster/dti")
```

## What?



## Why?



## How?

```{r, eval=FALSE}
library(dti)
```

### Bundle `AutoFill`

#### Default

See https://rstudio.github.io/DT/extensions.html (setion *1. AutoFill*)

With the AutoFill extension, you will see a blue square in the bottom-right corner of a cell when you mouse over the cell. You can drag it to automatically fill the column.

```{r}
mtcars %>% datatable2(bundle = dt_bundle_autofill())
```

```{r}
mtcars %>% datatable2(bundle = "AutoFill")
```

#### Custom options

For comparison when calling `DT::datatable()` 

```{r}
mtcars %>% DT::datatable(
    extensions = "AutoFill", 
    options = list(
        autoFill = TRUE
    )
)
```

```{r}
mtcars %>% datatable2(
    bundles = dt_bundle_autofill(columns = c(1, 2, 3))
)
```

```{r}
mtcars %>% datatable2(
    bundles = dt_bundle_autofill(columns = c(1, 2, 3), focus = "click")
)
```

```{r}
mtcars %>% datatable2(
    bundles = dt_bundle_autofill(
        columns = c("mpg", "disp"), 
        focus = "click",
        .data = mtcars
    )
)
```

```{r}
mtcars %>% datatable2(
    bundles = list(
        dt_bundle_autofill(
            .options = list(columns = c(1, 2, 3), focus = "click")
        )
    )
)
```

For comparison when calling `DT::datatable()` 

```{r}
mtcars %>% DT::datatable(
    extensions = "AutoFill", 
    options = list(
        autoFill = list(columns = c(1, 2, 3), focus = "click")
    )
)
```
